Appendix

### 2018-06-08 manuscript/appendix.Rmd
workout rayshader elevation map

test <- elevatr::get_elev_raster(as_Spatial(iws), z = 1)

>>>>

test <- elevatr::get_elev_raster(as_Spatial(iws), z = 8)
test2 <- crop(test, nws)

plot(test2)
plot(iws$geometry, add = TRUE)
plot(nws$geometry, add = TRUE)

test3 <- as.matrix(test2)
test4 <- rayshader::rayshade(test3, 
   anglebreaks = seq(55,65,10), 
   sunangle = 315, 
   maxsearch = 100)

ggplot(data = reshape2::melt(test4)) + 
  geom_tile(aes(x = Var1, y = Var2, fill = value)) +
  scale_fill_viridis_c() + 
  theme(legend.position = "none") + 
  theme_void()

image(test4)

test4 <- raster(test4)
crs(test4) <- crs(test2)

plot(test4)
plot(iws$geometry, add = TRUE)
